Reviewer Comments (Scientific Reports)

### 2020-03-24 notebook/sci_rep_reviews.Rmd
Make some edits to the response to Reviewer 2's comments

I appreciate these comments, and have tried to provide a more analytical explanation of the changes introduced by \gamma (L53-L64), including a new subsection explaining the effect of variation in $\gamma$ on the covariation of M (L65-L81). I agree that these analytical results improve the manuscript, and I think that they are particularly useful in setting the stage for the numerical simulations that now follow. In making these changes, I have slightly adjusted the notation so that the text is more readable.

@@

As suggested, I also considered matrices with even more structure, performing a new simulations on each. Specifically, I have simulated three broad classes of structured networks that are widespread in physical, social, and biological systems. These include food webs with cascade structures (e.g., Williams and Martinez 2000), small-world networks (Watts and Strogatz 1998), and scale-free networks (Albert and Barab\'{a}si 2002). Results for these networks are presented in L123-L140, and methods are explained in L247-L273, and in the Supplemental Information. Overall, these structured networks were affected by variation in $\gamma$ in the same way as random networks (increasing stability given sufficiently high complexity).

>>>>

I appreciate these comments, and have tried to provide a more analytical explanation of the changes introduced by \gamma (L53-L64), including a new subsection explaining the effect of variation in $\gamma$ on the (co)variation of M (L65-L81). I agree that these analytical results improve the manuscript, and I think that they are particularly useful in setting the stage for the numerical simulations that now follow. In making these changes, I have slightly adjusted the notation so that the text is more readable.

@@

As suggested, I also considered matrices with even more structure, performing new simulations on each. Specifically, I have simulated three broad classes of structured networks that are widespread in physical, social, and biological systems. These include food webs with cascade structures (e.g., Williams and Martinez 2000), small-world networks (Watts and Strogatz 1998), and scale-free networks (Albert and Barab\'{a}si 2002). Results for these networks are presented in L123-L140, and methods are explained in L247-L273, and in the Supplemental Information. Overall, these structured networks were affected by variation in $\gamma$ in the same way as random networks (increasing stability given sufficiently high complexity).
